---
title: "Chapter 2"
output: html_document
---


## Coding standards in R

1. Use a text editor / save as text file.
2. Indent your code (4-8 spaces recommended).
3. Limit the width (approx. 80 columns recommended).
4. Limit the length of individual functions. Ideally each function's code should be able to fit onto a single screen - this helps for readability and for debugging.

## Refresher on literate programming

The idea of literate programming comes from Don Knuth, Stanford.

How do I make my analysis reproducible? By deciding to do so and making efforts from the beginning.
- Store data in publicly available formats e.g. csv.
- Having entire pipeline stored in reproducible code means you have a regression test for your analysis - if it cannot be re-run with the same results then you know you have introduced an error.

Cons: can slow down the process by which you build a document. Can be hard to search through length code files to find explanatory text.

## Knitr

Good for

- Manuals
- Tutorials
- Reports

Not good for

- Long research articles with highly complex analysis - can be confusing to edit the documents.
- Work where complex / time-consuming computations are required.

### Processing of knitr documents

1. Write in Rmd
2. knitr produces markdown doc
3. knitr converts markdown to html

Never edit the md or html files.

#### Options

echo = FALSE  - doesn't show the code used to create output
results = "hide" - hides the output.

Using inline computations

```{r computetime}
time <- format(Sys.time(), "%a %b %d %X %Y")
rand <- rnorm(1)
```

The time this document was generated is `r time`. A random number is `r rand`.

#### Images / figures

These are included as raw data: inline in the html rather than links to the files - this is great in that the html exists as a standalone file.

#### Setting global options

Create a separate code chunk at the start of the document, and us `opts_chunk$set`. e.g.

```{r setoptions}
library(knitr)
opts_chunk$set(echo = FALSE)
```

#### Now we run more code to demonstrate it won't be echoed.
```{r printsomething}
print("Hello")
```

#### Useful common options

Output

- Results: "hide" / "asis". asis avoids applying html formatting to any r output.
- echo: T/F

Figures

- fig.height: numeric
- fig.width: numeric

#### Caching computations

Useful when one chunk takes a long time to run. 

Set `cache=T` to store results of computations on the disk for processing next time around.
If data / code or anything external changes, you'll have to run again, of course.